### 2016-09-01 Chapters/SolvationAndCorrelation.tex
Fix some missing references in CC chapter

I will present results on the formulation of quantum/classical
polarizable models when the quantum part of the system includes a
many-body description of electron correlation either by a \gls{MBPT},
\gls{CC} or hybrid approach.
These results leverage the variational formulation of quantum/classical
polarizable Hamiltonians described in Section \ref{sec:variational}.
This is an element of novelty with respect to the existing literature: I
will show how a fully variational framework enables transparent
derivations of \acrshort{MBPT} and \acrshort{CC} theory, encompassing previous
work~\cite{Cammi, Olivares del Valle, Caricato, Sneskov}
and solving some inconsistencies.~\cite{Angyan1992}

The contents of this Chapter are the result of an ongoing collaboration
with prof.~T.~Daniel Crawford (Virginia Tech) and Dr.~Andrew
C.~Simmonett (NIH)

After introducing the notation, I will derive the form of the \acrshort{CC}
effective Lagrangian and proceed to show how the work of
\citeauthor{Cammi2009-gu} and \citeauthor{Caricato2011-tx} on
\acrshort{PCM}-\acrshort{CC} and \citeauthor{Sneskov} on \acrshort{PE}-\acrshort{CC}
can easily be derived in the variational framework.

@@

\section{Effective Coupled Cluster Lagrangian}

@@

\section{Source terms in the classical energy functional}

>>>>

I will present results on the formulation of quantum/classical
polarizable models when the quantum part of the system includes a
many-body description of electron correlation either by a \gls{MBPT},
\gls{CC} or hybrid approach.
The contents of this Chapter are the result of an ongoing collaboration
with prof.~T.~Daniel Crawford (Virginia Tech) and Dr.~Andrew
C.~Simmonett (NIH)

I will leverage the variational formulation of quantum/classical
polarizable Hamiltonians described in Section \ref{sec:variational}.
This is an element of novelty with respect to the existing literature.
I will show how a fully variational framework enables transparent
derivations of \acrshort{MBPT} and \acrshort{CC} theory, encompassing
previous work~\autocite{Christiansen1999-tj, Cammi2009-gu,
Caricato2010-hx, Caricato2011-tx, Olivares_del_Valle1991-of,
Aguilar1991-vq, Olivares_del_Valle1991-tq, Olivares_del_Valle1993-xq,
Olivares_del_Valle1993-ra, Surjan1983-oc, Angyan1991-mr, Angyan1993-ay,
Angyan2008-nj, Nielsen2001-yl, Kongsted2003-py, Sneskov2010-dz,
Sneskov2011-jm, Schwabe2012-cf}
and solving some inconsistencies in the formulation of \acrshort{MBPT}
noted by \citeauthor{Angyan1995-co}.\autocite{Angyan1995-co,
Lipparini2009-io}

Sections \ref{sec:effective-cc-lagrangian} and \ref{sec:source-terms}
will introduce the effective \acrshort{CC} Lagrangian and the relevant
notation for the source terms in the classical energy functional,
respectively.
In Section \ref{sec:pcm-cc-models} I will derive the governing equation
for the effective Lagrangian and show how previous work on
continuum\autocite{Christiansen1999-tj, Cammi2009-gu, Caricato2011-tx}
and explicit models\autocite{Kongsted2003-py, Sneskov2011-jm} can easily
be derived in the variational framework.

@@

\section{Effective Coupled Cluster Lagrangian}
\label{sec:effective-cc-lagrangian}

@@

\section{Source Terms in the Classical Energy Functional}
\label{sec:source-terms}
